title: "ernakulam's climate vs covid numbers analysis"
author:"
output: html_notebook
---

```{r}
# Creating a dataframe
df <- read.csv("C:\\Users\\Jerome\\Downloads\\ernakulam (1).csv", header = TRUE)
df
```

```{r}
head(df)
```

```{r}
# To view data in tabular form
View(df)
```

```{r}
# Dimensions
dim(df)
```

```{r}
# To check the datatype of each column in df
str(df)
```

```{r}
summary(df)
```
```{r}
# Date column
str(df$DATE)
```


```{r}
# Converting to date format
x <- as.Date(df$DATE)
head(x)
class(x)
str(x)
```
```{r}
# Creating year, month, day columns
year <- as.numeric(format(x,'%Y'))
head(year)
month <- as.numeric(format(x,'%m'))
head(month)
day <- as.numeric(format(x,'%d'))
head(day)
```

```{r}
head(df)
```

```{r}
# Add columns to the existing df
df <- cbind(df,year,month,day)
head(df)
```

```{r}
summary(df)
```


```{r}
# Time Series - Germany's daily electricity consumption 
plot(df[,2], xlab = "day", ylab = "QV2M", type = 'l',
     main = "Pressure ", col = 'turquoise')
```

```{r}
# Solar
plot(df[,3], xlab = "day", ylab = "RH2M", type = 'l', main="Temperature", col = 'red')

```

```{r}
# Wind
plot(df [,4], xlab = "day", ylab = "PRECTOTCORR", type = 'l', main="Precipitation", col = 'yellow')
```

plot(df [,5], xlab = "day", ylab = "T2M", type = 'l', main="Precipitation", col = 'black')

```{r}
x <- as.Date(df$Date)
moddate <- as.Date(x, format = "%m/%d/%Y")
df2 <- cbind(moddate, df)
head(df2)
```

```{r}
df3 = subset(df2, subset = df2$moddate>='2016-01-01' & df2$moddate<='2016-12-31')
```

```{r}
plot(df3[,1], df3[,3], xlab = 'year', ylab = 'Daily Totals', type = 'l', main = 'Consumption', col = 'orange')
```

Time series plot for a specific year. We see the weekly oscillations in the above plot. There is also drastic decrease in electricity consumption in early Jan and late Dec during holidays.  

```{r}
plot(df3[,1], df3[,4], xlab = 'year', ylab = 'Daily Totals', type = 'l', main = 'Wind', col = 'green')
```
The wind production increases during winters as expected above. 
Hence verified for 2016.

```{r}
plot(df3[,1], df3[,5], xlab = 'year', ylab = 'Daily Totals', type = 'l', main = 'Solar', col = 'purple')
```

The Solar production increases during summers as expected. 